IRS County-to-County Migration Data

### 2018-08-08 manuscript_file.Rmd
Added the readme.

The R code used to produce these data is available in the **Supplementary Materials** and can also be found on github. The code makes use of multi-core processing to speed up computation time. Therer are three main sections in the code: A setup section; a data download section; and a data processing section. The final flat file, `county_migration_data.txt` can be either downloaded at github or produced by running the R code.

@@

# Usage Notes
Any origin-destination pair with fewer than 10 migrants over the entire period is excluded from the final datafile. This is done to reduce the size of the final datafile.

>>>>

The R code used to produce these data is available in the **Supplementary Materials** and can also be found on github. The code makes use of multi-core processing to speed up computation time. Therer are three main sections in the code: A setup section; a data download section; and a data processing section. The final flat file, `county_migration_data.txt`, contains the # of exemptions and can be either downloaded at github or produced by running the R code.

@@

# Usage Notes
Any origin-destination pair with fewer than 10 tax filers over the entire period is excluded from the final datafile. This is done to reduce the size of the final datafile.
